Mixture distribution data generation

### 2022-01-20 Ch3_samplesize/Datagen_viz.Rmd
Working on parameters for simulation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(fig.width=12, fig.height=6)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
#knitr::opts_chunk$set(fig.width=12, fig.height=6)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

@@

Thinking that to parameterize the distributions for the simulation in Ch3, I could use the fits from Ch2 under the PP model with the lognormal distribution:

```{r}
# Some theme stuff

library(MetBrewer)

sgroup_col <- met.brewer("Tiepolo", n = 7)
aval <- 0.3

figx.theme <- theme_bw() +
  theme(legend.position = "right",
        axis.title = element_text(size = 8))

# Select only the PP lnorm data
pp.boot.fits %>%
  #filter(., dBIC == 0) %>% 
  filter(., dist == "lnorm") %>% 
  dplyr::select(group, boot, estimate, param, dist) %>% 
  pivot_wider(names_from = param, values_from = estimate) %>% 
  mutate(group = as.factor(group)) -> lnpp.params

lnpp.params %>% 
  ggplot(., aes(x = meanlog, y = sdlog, color = group)) +
    geom_point(alpha = aval) +
    scale_color_manual(values=sgroup_col, drop=FALSE) +
    lims(x = c(0.7, 3.7), y = c(0.5, 2.1)) +
    labs(subtitle = "PP - lnorm") +
    figx.theme +
  guides(color = guide_legend(title = "Group", override.aes = list(alpha = 1, size = 5)))

```

```{r}
# Use the parameters from the figure above to simulate data?

lnpp.params %>% 
  group_by(group) %>% 
  summarise(meanlogs = median(meanlog),
            sdlogs = median(sdlog)) -> logparams

meanlogs <- logparams$meanlogs
sdlogs <- logparams$sdlogs

density_curves <- purrr::map(1:7, function(y) stat_function(fun = dlnorm,
                                                            args = list(meanlog = meanlogs[y], sdlog = sdlogs[y]),
                                                            color = sgroup_col[y]))

ggplot() +
  density_curves +
  figx.theme +
  lims(x = c(0, 30), y = c(0, 0.2))

```

Using base R

```{r}
meanlogs <- c(3.011376, 2.670338, 2.842328, 2.830963, 1.637819, 2.351636, 2.117476)
sdlogs <- c(1.343584, 1.114171, 1.032824, 1.010781, 1.487352, 1.139045, 1.150798)

xs <- seq(0,20, by = 0.1)

par(mfrow=c(2,1))
plot(xs, dlnorm(x = xs, meanlog = meanlogs[1], sdlog = sdlogs[1]), type = "l", col = "grey", ylab = "Density")
points(xs, dlnorm(x = xs, meanlog = meanlogs[2], sdlog = sdlogs[2]), type = "l", col = "grey")
points(xs, dlnorm(x = xs, meanlog = meanlogs[3], sdlog = sdlogs[3]), type = "l", col = "grey")
points(xs, dlnorm(x = xs, meanlog = meanlogs[4], sdlog = sdlogs[4]), type = "l", col = "grey")
points(xs, dlnorm(x = xs, meanlog = meanlogs[5], sdlog = sdlogs[5]), type = "l", col = "grey")
points(xs, dlnorm(x = xs, meanlog = meanlogs[6], sdlog = sdlogs[6]), type = "l", col = "grey")
points(xs, dlnorm(x = xs, meanlog = meanlogs[7], sdlog = sdlogs[7]), type = "l", col = "grey")

```
